### 2021-04-11 paper/ase21/analyzer.tex
[ASE21] Added subtype figure
[ASE21] A small change in 3.1

$\ires$ is an untyped intermediate representation introduced by \citet{jiset}.
For brevity, we formally define a modified $\ires$ as follows:
\[
  \begin{array}{lr@{~}r@{~}l}
    \text{Instructions}
    & \inst &::=&
    \kwlet \; \x = \expr \mid
    \kwlet \; \x = \kwrl \expr \; \expr^* \kwrr \mid
    \kwassert \; \expr \\

    &&\mid&
    \kwif \; \expr \; \lab \; \lab \mid
    \kwreturn \; \expr \mid
    \refer = \expr \\

    \text{References}
    & \refer &::=&
    \x \mid
    \refer \kwsl \expr \kwsr \\

    \text{Expressions}
    & \expr &::=&
    \tname \kwcl [\x \kwarrow \expr]^* \kwcr \mid
    \expr: \ty \mid
    \refer \kwexists \mid
    \expr \bop \expr \mid
    \uop \expr \mid
    \refer \mid
    \const \mid
    \prim \\

    \text{Primitives}
    & \prim &::=&
    \undefval \mid \nullval \mid \bool \mid
    \num \mid \bigint \mid \str \mid \symb \\

    \text{Types}
    & \ty &::=& \tname \mid \tjs \mid \tprim \mid
    \undefval \mid \nullval \mid \tbool\\

    &&\mid&
    \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
  \end{array}
\]
A modified $\ires$ program $\prog = (\getlab, \nextlab)$ is a pair of two finite
mappings. The getter mapping $\getlab: \labset \finmap \instset$ represents
instructions attached to labels, and the next mapping $\nextlab: \labset \finmap
\labset$ denotes next labels. A label $\lab \in \labset$ denotes a program
point.  An instruction $\inst$ is a variable declaration, a function call, an
assertion, a branch, a return, or an reference update.  Each invocation of an
abstract algorithm in ECMAScript is compiled to a function call instruction with
a newly introduced temporal variable.  We represent loops using branch
instructions with cyclic pointing of labels in the next mapping $\nextlab$.  A
reference $\refer$ is a variable $\x$ or a field access $\refer \kwsl \expr
\kwsr$.  An expression $\expr$ is a record, a type check, an existence check, a
binary operation, a unary operation, a reference, a constant, or a primitive,
which is either $\undefval$, $\nullval$, a Boolean $\bool$, a Number $\num$, a
BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{img/overall}
  \vspace*{-1.5em}
  \caption{The subtype relation $\subtype$ between types.}
  \label{fig:subtype}
  \vspace*{-1.5em}
\end{figure}

A type $\ty \in \tyset$ is a norminal type $\tname$ or a pre-defined type;
$\tjs$ denotes JavaScript values, $\tprim$ primitives, $\tnumeric$ either Number
or BigInt values, and $\tnum$, $\tbigint$, $\tstr$, and $\tsymb$ denote Number,
BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is a
production name for ASTs or a record type name used in abstract algorithms.  The
subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
described in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  For
example, \inred{name and subtype example using 14.1.19 in Figure 2}.  Based on
this subtype relation, a type check expression $\expr: \ty$ checks whether the
evaluation result of $\expr$ has a type $\ty' \subtype \ty$.

@@

>>>>

$\ires$ is an untyped intermediate representation introduced by \citet{jiset}.
To make it more suitable for type analysis, we modify it as a label-based
language as follows:
\[
  \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
    \text{Functions}
    &\funcset&\ni&\func&::=&\kwdef \; \x (\x^*, \x^*). \; \lab\\

    \text{Instructions}
    &\instset&\ni&\inst&::=&
    \kwlet \; \x = \expr \mid
    \kwlet \; \x = \kwrl \expr \; \expr^* \kwrr \mid
    \kwassert \; \expr \\

    &&&&\mid&
    \kwif \; \expr \; \lab \; \lab \mid
    \kwreturn \; \expr \mid
    \refer = \expr \\

    \text{References}
    &&&\refer&::=&
    \x \mid
    \refer \kwsl \expr \kwsr \\

    \text{Expressions}
    &&&\expr&::=&
    \tname^? \; \kwcl [\x: \expr]^* \kwcr \mid
    \kwsl \expr^* \kwsr \mid
    \expr: \ty \mid
    \refer \kwexists \\

    &&&&\mid&
    \expr \bop \expr \mid
    \uop \; \expr \mid
    \refer \mid
    \const \mid
    \prim \\

    \text{Primitives}
    &\primset&\ni&\prim&::=&
    \undefval \mid \nullval \mid \bool \mid
    \num \mid \bigint \mid \str \mid \symb \\

    \text{Types}
    &\tyset&\ni&\ty&::=&\tname \mid \tjs \mid \tprim \mid
    \undefval \mid \nullval \mid \tbool\\

    &&&&\mid&
    \tnumeric \mid \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
  \end{array}
\]
A modified $\ires$ program $\prog = (\funcs, \getlab, \nextlab)$ is a triple of
a set of functions $\funcs \subseteq \and \funcset$ and two finite mappings
$\getlab$ and $nextlab$.  The getter mapping $\getlab: \labset \finmap \instset$
represents instructions attached to labels, and the next mapping $\nextlab:
\labset \finmap \labset$ denotes next labels.  A function $\kwdef \; \f (\x^*,
\y^*). \; \lab \in \funcset$ consists of a name $\f$, normal parameters $\x^*$,
optional parameters $\y^*$, and a body label $\lab$.  A label $\lab \in \labset$
denotes a program point.  An instruction $\inst$ is a variable declaration, a
function call, an assertion, a branch, a return, or an reference update.  Each
invocation of an abstract algorithm in ECMAScript is compiled to a function call
instruction with a newly introduced temporal variable.  We represent loops using
branch instructions with cyclic pointing of labels in the next mapping
$\nextlab$.  A reference $\refer$ is a variable $\x$ or a field access $\refer
\kwsl \expr \kwsr$.  An expression $\expr$ is a record, a list, a type check, an
existence check, a binary operation, a unary operation, a reference, a constant,
or a primitive, which is either $\undefval$, $\nullval$, a Boolean $\bool$, a
Number $\num$, a BigInt $\bigint$, a String $\str$, or a Symbol $\symb$.

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{img/subtype}
  \vspace*{-1.5em}
  \caption{A graphical representation of subtype relation $\subtype$.}
  \label{fig:subtype}
  \vspace*{-1.5em}
\end{figure}

A type $\ty \in \tyset$ is a norminal type $\tname$ or a pre-defined type;
$\tjs$ denotes JavaScript values, $\tprim$ primitives, $\tnumeric$ either Number
or BigInt values, and $\tnum$, $\tbigint$, $\tstr$, and $\tsymb$ denote Number,
BigInt, String, and Symbol values, respectively.  A norminal type $\tname$ is a
production name for ASTs or a record type name used in abstract algorithms.  The
subtype relation $\subtype \subseteq \tyset \times \tyset$ between types is
described in Figure~\ref{fig:subtype}; the directed edge from $\ty'$ to $\ty$
denotes $\ty' \subtype \ty$ and the relation is reflexive and transitive.  The
subtype relation is dependent on the syntax and defined record types in
ECMAScript.  We manually model subtypes between record types but automatically
extract subtypes for AST types.  For example, consider the syntax-directed
abstract algorithm at the right bottom in Figure~\ref{fig:example}.  The
non-terminal \textit{BindingElement} is the unique token in a alternative of
\textit{FormalParameter} thus we automatically extract the subtype relation:
\textit{BindingElement} $\subtype$ \textit{FormalParameter}.  Based on this
subtype relation, a type check expression $\expr: \ty$ checks whether the
evaluation result of $\expr$ has a type $\ty'$ satisfying $\ty' \subtype \ty$.
We represent semantics of the modified $\ires$ as a state transition system
$(\stset, \trans, \istset)$ with the transition relation $\trans \subseteq
\stset \times \stset$.  For presentation brevity, we omit its detail in this
paper and include it in a companion report~\inred{\cite{report}}.
% \[
%   \begin{array}{l@{~}r@{~}c@{~}r@{~}r@{~}l}
%     \text{States}
%     &\st&\in&\stset&::=&\ctxtset^* \times \labset \times \envset\\
% 
%     \text{Contexts}
%     &\ctxt$\in$\ctxtset&::=&\labset \times \varset \times \envset\\
% 
%     \text{Environments}
%     &\env$\in$\envset&::=&\varset \finmap \valset\\
% 
%     \text{Values}
%     &\val$\in$\valset&::=& \addrset \uplus \addr \uplus \primset\\\
%   \end{array}
% \]

@@

Abstract Interpretation~\cite{ai1977, ai1992}

\begin{figure*}[t]
  \centering
  \[
    \todo
  \]
  \vspace*{-1em}
  \caption{Abstract .}
  \label{fig:example}
\end{figure*}

### 2021-04-11 paper/ase21/intro.tex
[ASE21] A small change in 3.1

For the compiled mechanized specifications, $\tool$ performs type analysis for
compiled functions with specification types defined in ECMAScript.  ECMAScript
contains not only JavaScript language types but also specification types such as
abstract syntax trees (ASTs), internal records (i.e. environments, completions,
or property descriptors), and internal lists.  Our tool extract syntax and
table-based type information from ECMAScript and constructs type hierarchy and
fields for ASTs and records.  Based on the extracted types, $\tool$ performs
type analysis and detects specification bugs using a \textit{bug detector}
consisting of four different checkers: 1) reference checker, 2) arity checker,
and 3) assertion checker, 4) operand type checker.  Moreover, to increase
precision of type analysis, we also present \textit{condition-based refinement}
for type analysis on ECMAScript. Its main concept is to prunes out infeasible
abstract states by using conditions of assertions and branches.  The refinement
technique can reduce false alarms caused by spurious types inferred by imprecise
analysis.  We evaluate our tool with all \inred{XXX} different versions existed
in the official ECMAScript repository for the recent \inred{three years from
2018 to 2021}.

>>>>

For the compiled mechanized specifications, $\tool$ performs type analysis for
compiled functions with specification types defined in ECMAScript.  ECMAScript
contains not only JavaScript language types but also specification types such as
abstract syntax trees (ASTs), internal records (i.e. environments, completions,
or property descriptors), and internal list-like structures.  Our tool extract
syntax and table-based type information from ECMAScript and constructs type
hierarchy and fields for ASTs and records.  Based on the extracted types,
$\tool$ performs type analysis and detects specification bugs using a
\textit{bug detector} consisting of four different checkers: 1) reference
checker, 2) arity checker, and 3) assertion checker, 4) operand type checker.
Moreover, to increase precision of type analysis, we also present
\textit{condition-based refinement} for type analysis on ECMAScript. Its main
concept is to prunes out infeasible abstract states by using conditions of
assertions and branches.  The refinement technique can reduce false alarms
caused by spurious types inferred by imprecise analysis.  We evaluate our tool
with all \inred{XXX} different versions existed in the official ECMAScript
repository for the recent \inred{three years from 2018 to 2021}.
